Plots for Latent Hawkes Paper

### 2020-11-17 output_scripts/Paper_Plots.Rmd
correct typo in glicko ranks and begin creating plot for this

@@

  m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  if(length(prob_id) != 0) {
    m3_pr <- m3_pr[-prob_id,-prob_id]
  }
  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/immhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  print(range(as.vector(indep_pr)))
  if(length(prob_id) != 0) {
    indep_pr <- indep_pr[-prob_id,-prob_id]
  }
  if(current_cohort == 10) {
    # one additional row
    # print("in here")
    new_prob_row <- which(rowSums(m1_pr) == 0)
    new_prob_col <- which(colSums(m1_pr) == 0)
    prob_id <- c(new_prob_row,new_prob_col) 
    if(length(prob_id) != 0) {
      m1_pr <- m1_pr[-prob_id, -prob_id]
      m2_pr <- m2_pr[-prob_id, -prob_id]
      m3_pr <- m3_pr[-prob_id, -prob_id]
      indep_pr <- indep_pr[-prob_id, -prob_id]
    }
  }

  m1_score <-positiveNegativeApproxError(m1_pr)
  m2_score <- positiveNegativeApproxError(m2_pr)
  m3_score <- positiveNegativeApproxError(m3_pr) ## smallest value which is good
  ind_score <- positiveNegativeApproxError(indep_pr) 
  ## this doesn't make sense because all negative
  ## values
  current_score <- tibble(m1_score, m2_score, m3_score, ind_score)
  names(current_score) <- c("C-HP","C-DCHP","C-MMHP","I-MMHP")
  current_score$type <- c("Positive","Negative")
  current_score$Cohort <- current_cohort
  struct_scores <-struct_scores %>% bind_rows(current_score)
}

struct_scores %>% 
  rename(Pos_Neg = type) %>%
  pivot_longer(cols = "C-HP":"I-MMHP",
               names_to = "Method", values_to = "Score") %>%
  filter(Score > 0) %>%
  filter(!(Method == "ind_score" & Pos_Neg == "Positive")) %>%
  ggplot(aes(Method,Score)) + geom_boxplot() +
  facet_wrap(~Pos_Neg) + theme_minimal()

>>>>

# Figure 5b: Simulation Spearman Rank

@@

  m3_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/cmmhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  if(length(prob_id) != 0) {
    m3_pr <- m3_pr[-prob_id,-prob_id]
  }
  indep_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                       "/immhp_pr_matrix_",cohort_names[current_cohort],
                       ".RDS",sep=''))
  # print(range(as.vector(indep_pr)))
  if(length(prob_id) != 0) {
    indep_pr <- indep_pr[-prob_id,-prob_id]
  }
  if(current_cohort == 10) {
    # one additional row
    # print("in here")
    new_prob_row <- which(rowSums(m1_pr) == 0)
    new_prob_col <- which(colSums(m1_pr) == 0)
    prob_id <- c(new_prob_row,new_prob_col) 
    if(length(prob_id) != 0) {
      m1_pr <- m1_pr[-prob_id, -prob_id]
      m2_pr <- m2_pr[-prob_id, -prob_id]
      m3_pr <- m3_pr[-prob_id, -prob_id]
      indep_pr <- indep_pr[-prob_id, -prob_id]
    }
  }

  m1_score <-positiveNegativeApproxError(m1_pr)
  m2_score <- positiveNegativeApproxError(m2_pr)
  m3_score <- positiveNegativeApproxError(m3_pr) ## smallest value which is good
  ind_score <- positiveNegativeApproxError(indep_pr) 
  ## this doesn't make sense because all negative
  ## values
  current_score <- tibble(m1_score, m2_score, m3_score, ind_score)
  names(current_score) <- c("C-HP","C-DCHP","C-MMHP","I-MMHP")
  current_score$type <- c("Positive Residuals","Negative Residuals")
  current_score$Cohort <- current_cohort
  struct_scores <-struct_scores %>% bind_rows(current_score)
}

struct_plot <- struct_scores %>% 
  rename(Pos_Neg = type) %>%
  pivot_longer(cols = "C-HP":"I-MMHP",
               names_to = "Method", values_to = "Score") %>%
  filter(Score > 0) %>%
  filter(!(Method == "I-MMHP" & Pos_Neg == "Positive"))
  # mutate(Method = as.factor(Method, levels = c("I-MMHP","C-HP","C-DCHP",
  #                                              "C-MMHP"))) %>%
struct_plot$Method <- factor(struct_plot$Method, levels = c("I-MMHP","C-HP","C-DCHP",
                                               "C-MMHP") )

struct_plot %>% 
  ggplot(aes(Method,Score)) + geom_boxplot() +
  facet_wrap(~Pos_Neg, scales = "free") + theme_minimal()
